Pyrovelocity PyPI user notebook template

### 2024-03-21 scripts/examples/pypi_template/pyrovelocity_pypi_user_template.qmd
fix(pypi_template): remove unnecessary output capture Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```{python}
#| label: execute-summarize-data-task
#| output: false
from IPython.utils import io

with io.capture_output() as captured:
  dataset_summary = summarize_data(
    preprocess_data_args=pancreas_configuration.preprocess_data,
    postprocessing_outputs=postprocessing_outputs,
    training_outputs=model_output,
  )
```

>>>>

```{python}
#| label: execute-summarize-data-task
#| output: false
dataset_summary = summarize_data(
  preprocess_data_args=pancreas_configuration.preprocess_data,
  postprocessing_outputs=postprocessing_outputs,
  training_outputs=model_output,
)
```
